\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-17 proof-no-distributed.tex
Finished writing major proofs and fixing references. Still needs a once through

Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta) = \eta(0)$. 
%
Since $B_1,B_2,\ldots$ satisfy the conditions in Theorem~\ref{thm:LAN1}, $\theta$ is in $\Xi$ if and only if
\begin{equation}
\label{eq:non_existence_proof}
\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0). 
\end{equation}
By assumption, we have $B_i^{-1} = A_i$ where $A_i$ can be expressed as
\[
A_i = \cup_{i=1}^K (a_{i,k},b_{i,k}), 
\]
where $a_{i,1} \leq b_{i,1} \leq \ldots \leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values $-\infty$ and $\infty$, respectively. Denote
\[
C_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\}.
\]
For any $\theta$ and $\epsilon>0$, denote 
\[
S_n(\theta, \epsilon) \triangleq \left\{ i\leq n \,:\, (\theta-\epsilon,\theta+\epsilon) \cap C_i \neq \emptyset \right\}
\]
In words, $S_n$ contains all integers smaller than $n$ in which an $\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals consisting $A_i$. 
%
We now claim that 
if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
\begin{align}
& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
& 
+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
& \overset{(a)}{\leq}
\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
 \label{eq:non_existence_proof1}
\end{align}
where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
\[
\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
\]
Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$. \par
For $k\in \N$, assume by contradiction that there exists $N \geq 2K + 1$ distinct elements
$\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$ consists of at most $K$ intervals, we have that 
\begin{equation}
\label{eq:few_optimality_points_proof}
\card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
\end{equation}
Fix $\epsilon>0$ such that 
\[
\epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
\]
Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
\[
\card \left(S_n(\theta_i, \epsilon) \right) \geq n \left(1-\frac{1}{2N} \right)
\]
for all $i=1,\ldots,N$. However, $S_n(\theta_1,\epsilon), \ldots S_n(\theta_N,\epsilon)$ are disjoint, so the cardinallity of their union is at least $n\left(1-\frac{1}{2N} \right)N$ which is grater than $2nK + n/2$ in contradiction to \eqref{eq:few_optimality_points_proof}.

>>>>

Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta)
= \eta(0)$.
%
Since $B_1,B_2,\ldots$ satisfy the conditions in
Theorem~\ref{theorem:non-adaptive-minimax}, $\theta$ is in $\Xi$ if and only
if $\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0)$.  By
assumption, we have $B_i = \indic{X_i \in A_i}$ where each $A_i =
\cup_{i=1}^K \{[a_{i,k},b_{i,k}]\}$, where $a_{i,1} \leq b_{i,1} \leq \ldots
\leq a_{i,K}, b_{i,K}$, and $a_{i,1}$ and $b_{i,K}$ may take the values
$-\infty$ and $\infty$, respectively. Denote the endpoints
\begin{equation*}
  E_i = \cup_{k=1}^{K}\{a_{i,k},b_{i,k}\},
\end{equation*}
and for $\theta$ and $\epsilon>0$, define
\begin{equation*}
  S_n(\theta, \epsilon) \triangleq \left\{ i\leq n ~ \mbox{s.t.}~
  (\theta-\epsilon,\theta+\epsilon) \cap E_i \neq \emptyset \right\}
\end{equation*}
In words, $S_n$ contains all integers smaller than $n$ in which an
$\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals
defining $A_i$.
%
We now claim that 
if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
\begin{align}
& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
\frac{ \left(\sum_{k=1}^{K}  f(\theta - b_{i,k})- f(\theta - a_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
& 
+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(b_{i,k}-\theta) - f(a_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - b_{i,k})- F(\theta - a_{i,k}) \right)\right)} \nonumber \\
& \overset{(a)}{\leq}
\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
 \label{eq:non_existence_proof1}
\end{align}
where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
\begin{equation*}
\max\left\{ \max_k \eta(b_{i,k}-\theta) , \max_k \eta(a_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
\end{equation*}
Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.

Assume for the sake of contradiction that there exists $N \geq 2K + 1$
distinct elements $\theta_1,\ldots,\theta_N \in \Xi$. Since each $A_i$
consists of at most $K$ intervals, we have that
\begin{equation}
  \label{eq:few_optimality_points_proof}
  \card (\cup_{i=1}^n \mathcal B_i) \leq 2 n K. 
\end{equation}
Fix $\epsilon>0$ such that 
\begin{equation*}
  \epsilon < \frac{1}{2}\min_{i\neq j} |\theta_i - \theta_j|. 
\end{equation*}
Since for each $\theta \in \Theta$ we have $S_n(\theta, \epsilon) \to 1$, there exists $n$ large enough such that 
\begin{equation*}
  \card \left(S_n(\theta_i, \epsilon) \right)
  \geq n \left(1-\frac{1}{2N} \right)
\end{equation*}
for all $i=1,\ldots,N$. However, $S_n(\theta_1,\epsilon), \ldots
S_n(\theta_N,\epsilon)$ are disjoint, so the cardinality of their union is
at least $n\left(1-\frac{1}{2N} \right)N > 2nK + n/2$, a contradiction to
inequality~\eqref{eq:few_optimality_points_proof}.

### 2019-12-17 proof-sgd.tex
Rewrote entire proof of local asymptotic normality
Finished writing major proofs and fixing references. Still needs a once through

\providecommand{\score}{\dot{\ell}}

@@

We apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
$\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
The update~\eqref{eq:polyak_new_measurements} gives
\begin{align*} 
  U_n %% & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
  & = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
\end{align*}
so the estimator $\bar{U}_n$ is identical to the stochastic gradient
estimator~\eqref{eq:sgd_est}. We have $\E[\varphi(x + Z)^4] = 1$ and by
assumption the Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the
functions $\psi$ and $\chi$ have the desired conditions of
Corollary~\ref{corollary:polyak-juditsky} (as we verify in
Section~\ref{sec:proof-normal-sgd}). Finally, the function $\theta \mapsto
\E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
that for $x^\star = \theta$ and $g'' \equiv 1$, we may apply
Corollary~\ref{corollary:polyak-mse} and a finite approximation to the prior
measure $\pi$ to obtain
Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.

@@

The regularity result~\eqref{eq:normal_expansion_lem} gives
\begin{equation*}
  \sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}}
  \sum_{i = 1}^n  \frac{\varphi(Z_i)}{\psi'(0)} + o_{P,n}(1).
\end{equation*}
The conditions in
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam} imply
that the Fisher information $I_h =
\E_h[\score_h(Z)^2]$ exists and is continuous for
$\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
and the asymptotic expansion~\eqref{eqn:lan-from-qmd}
with the preceding display give the joint convergence
\begin{equation*}
  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
  \right)
  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
  \begin{pmatrix}
    \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
    \E_p[\varphi(Z) \score_0(Z)] \\
    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
    & h^2 I_0
  \end{pmatrix}  \right).
\end{equation*}
Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
convergence
\begin{equation*}
  \sqrt{n}\bar{\Delta}_n
  \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
  \Ncal\left(\frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score(Z)],
  \frac{\chi(0)}{\psi'(0)^2} \right)
\end{equation*}
under the alternatives $P_{h_n/\sqrt{n}}$, which gives
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.

>>>>

@@

We apply Corollary~\ref{corollary:polyak-mse} with $g(x) = 0.5(x-\theta)^2$,
$\varphi(x) = \sgn(x)$, $Z_n = \theta-X_n$.
The update~\eqref{eq:polyak_new_measurements} gives
\begin{align*} 
  U_n %% & = U_{n-1} + \gamma_n \sgn(\theta-U_{n-1} - Z_n )  \\
  & = U_{n-1} + \gamma_n \sgn(X_n-U_{n-1} ),
\end{align*}
so the estimator $\bar{U}_n$ is identical to the stochastic gradient
estimator~\eqref{eq:sgd_alg} with $\bar{\theta}_n = \frac{1}{n} \sum_{i =
  1}^n \theta_i$. We have $\E[\varphi(x + Z)^4] = 1$ and by assumption the
Fisher information $\E[(f'(Z))^2 / f(Z)^2]$ exists, and the functions $\psi$
and $\chi$ have the desired conditions of
Corollary~\ref{corollary:polyak-juditsky} (as we verify in
Section~\ref{sec:proof-normal-sgd}). Finally, the function $\theta \mapsto
\E_{P_\theta}[(\bar{\theta}_n - \theta)^2]$ is continuous in $\theta$, so
that for $x^\star = \theta$ and $g'' \equiv 1$, we may apply
Corollary~\ref{corollary:polyak-mse} and a finite approximation to the prior
measure $\pi$ to obtain
Theorem~\ref{thm:sgd}\eqref{item:sgd-ms-convergence}.

@@

The regularity result~\eqref{eq:normal_expansion_lem} gives
\begin{equation*}
  \sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}}
  \sum_{i = 1}^n  \frac{\varphi(Z_i)}{\psi'(0)} + o_{P,n}(1).
\end{equation*}
The conditions in
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam} imply
that the Fisher information $I_h =
\E_h[\score_h(Z)^2]$ exists and is continuous for
$\score_h(z) = \frac{p'(z - h)}{p(z - h)}$,
and the asymptotic expansion Definitions~\ref{definition:qmd}
and~\ref{definition:lan} allow combines
with the preceding display to give the joint convergence
\begin{equation*}
  \left(\sqrt{n} \bar{\Delta}_n, \log \frac{P^n_{h_n/\sqrt{n}}}{P^n_0}(Z_1^n)
  \right)
  \cd \normal \left( \left(0,-\frac{h^2}{2} I_0 \right),
  \begin{pmatrix}
    \frac{\chi(0)}{\psi'(0)^2} & \frac{-h}{ \psi'(0)}
    \E_p[\varphi(Z) \score_0(Z)] \\
    \frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score_0(Z)]
    & h^2 I_0
  \end{pmatrix}  \right).
\end{equation*}
Le Cam's third lemma \cite[Exm. 6.7]{VanDerVaart98} then implies the
convergence
\begin{equation*}
  \sqrt{n}\bar{\Delta}_n
  \mathop{\cd}_{P_{h_n/\sqrt{n}}^n}
  \Ncal\left(\frac{-h}{ \psi'(0)} \E_p[\varphi(Z) \score(Z)],
  \frac{\chi(0)}{\psi'(0)^2} \right)
\end{equation*}
under the alternatives $P_{h_n/\sqrt{n}}$, which gives
Corollary~\ref{corollary:normal-expansion}\eqref{item:apply-le-cam}.
